---
title: "Height Diameter Models"
author: "Maximiliane Jousse"
date: "May 2023"
output: html_document
---

Using existing data from tree inventory plots in 1) Sardinilla, and 2) Lake Bayano Area (Ipeti), we relate DBH (diameter at breast height; cm) to height (m) with glms. Results are compared with Chave's equation ()

```{r, include=FALSE}

library(data.table)
library(tidyr)
library(dplyr)
library(ggplot2)
library(readxl)
library(broom)
library(cowplot)
library(viridis)
library(glue)
library(ggpubr)

```

# Sardinilla Data

```{r, echo = FALSE}
s_data <- read_excel("../Data/MJ_SARDINILLA_ALL_YEARS.xlsx")
```

## Data Exploration

```{r, echo = FALSE}
head(s_data)

# remove dead trees
s_data <- s_data %>% filter(Status != "Dead")

```

## Data Visualization

```{r, echo = FALSE}
#DBH
s_data %>% 
  select(SpeciesCode, Height, DBH)%>%
  drop_na() %>%
  ggplot(aes(x = DBH, y = Height, color = SpeciesCode)) +
  geom_point()+
  xlab("DBH (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH Sardinilla")
```

```{r, echo = FALSE}
s_data %>% 
  select(SpeciesCode, Height, DBH) %>%
  mutate(lDBH = log(DBH), lHeight = log(Height))%>%
  drop_na() %>%
  ggplot(aes(x = lDBH, y = lHeight, color = SpeciesCode)) +
  geom_point()+
  xlab("ln(DBH)") +
  ylab("ln(Height)") +
  ggtitle("ln(Height) vs ln(DBH) Sardinilla")
```

```{r, echo = FALSE}
#DBH ln(height) vs dbh
# CLEAREST PATTERN, LESS SPREAD
s_data %>% 
  select(SpeciesCode, Height, DBH) %>%
  mutate(lHeight = log(Height))%>%
  drop_na() %>%
  ggplot(aes(x = DBH, y = lHeight, color = SpeciesCode)) +
  geom_point()+
  xlab("DBH") +
  ylab("ln(Height)") +
  ggtitle("ln(Height) vs DBH Sardinilla")
```

```{r, echo = FALSE}
#DBH, separate species
s_data %>% 
  select(SpeciesCode, Height, DBH)%>%
  drop_na() %>%
  ggplot(aes(x = DBH, y = Height)) +
  geom_point()+
  facet_grid(cols = vars(SpeciesCode))+
  xlab("DBH (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH Sardinilla")
```

```{r, echo=FALSE}
# ln(Height)-DBH, seperate species
s_data %>% 
  select(SpeciesCode, Height, DBH) %>%
  mutate(lHeight = log(Height))%>%
  drop_na() %>%
  ggplot(aes(x = DBH, y = lHeight, color = SpeciesCode)) +
  geom_point()+
  xlab("DBH") +
  ylab("ln(Height)") +
  ggtitle("ln(Height) vs DBH Sardinilla")+
  facet_grid(cols = vars(SpeciesCode))
```

Using Basal Diameter:

```{r, echo = FALSE}
s_data %>% 
  select(SpeciesCode, Height, BasalDiam)%>%
  drop_na() %>%
  ggplot(aes(x = BasalDiam, y = Height, color = SpeciesCode)) +
  geom_point()+
  xlab("Basal diameter (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH Sardinilla")
```

```{r, echo = FALSE}
#BasalDiam, separate species
#         defo more linear
s_data %>% 
  select(SpeciesCode, Height, BasalDiam)%>%
  drop_na() %>%
  ggplot(aes(x = BasalDiam, y = Height)) +
  geom_point()+
  facet_grid(cols = vars(SpeciesCode))+
  xlab("Basal Diam (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH Sardinilla")
```

### SUMMARY

The clearest pattern is seen in ln(height) vs DBH.

## Testing Regressions

### Chave's Equation (as a comparaison)

```{r}
chaveTest <- function(D) {
  lH <- 0.893 + 0.02418293 + 0.760*log(D) - 0.0340*((log(D))^2)
  # chaves equation gives height in in m
  return(lH)
}
```

### a: all species, DBH, Linear Height DBH regression

```{r}
s_data %>% 
  select(SpeciesCode, Height, DBH)%>%
  drop_na() %>%
  ggplot(aes(x = DBH, y = Height)) +
  geom_point()+
  geom_smooth(method = "lm")+
  xlab("DBH (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH Sardinilla")
```

### b:Each species, DBH, Linear Height DBH regression

```{r}
s_data %>% 
  select(SpeciesCode, Height, DBH)%>%
  drop_na() %>%
  ggplot(aes(x = DBH, y = Height)) +
  geom_point()+
  geom_smooth(method = "lm")+
  facet_grid(cols= vars(SpeciesCode)) +
  xlab("DBH (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH Sardinilla")
```

### c: all species, DBH, Quadratic - fit a quadratic lm for log(height)-diameter

```{r}
s_data$DBH2 <- s_data$DBH^2
glm1 <- lm(log(Height)~DBH+DBH2, data = s_data)
```

```{r, echo = FALSE}
s_data %>%
  select(Height, DBH, SpeciesCode) %>%
  drop_na() %>%
  mutate(glm1fit = exp(fitted(glm1))) %>%
  ggplot(aes(x=DBH))+
  geom_point(aes(y=Height))+
  geom_line(aes(y=glm1fit), linetype = "dashed", color = "red")
```

Doesn't work: parabola falls off

### d: all species, DBH, fit lm for log(height)-log(diameter)

This model is the CURRENT BEST

```{r}
s_data$lDBH <- log(s_data$DBH)
s_data$lDBH2 <- s_data$lDBH^2
#quadratic
glm2q <- lm(log(Height)~lDBH + lDBH2, data = s_data)
#linear
glm2l <- lm(log(Height)~lDBH, data = s_data)
```

```{r, echo = FALSE}
#looking at both
s_data %>%
  select(Height, DBH, lDBH, SpeciesCode) %>%
  drop_na() %>%
  mutate(lHeight = log(Height), glmfit1 = fitted(glm2q), glmfit2 = fitted(glm2l)) %>%
  ggplot(aes(x=DBH))+
  geom_point(aes(y=lHeight))+
  geom_line(aes(y=glmfit1), linetype = "dashed", color = "red")+
  geom_line(aes(y = glmfit2), color = 'blue')

```

```{r}
#best - glm2l
glm2 <- lm(log(Height)~lDBH, data = s_data) # Equivalent to glm2l
```

```{r, echo = FALSE}
s_data %>%
  select(Height, DBH, lDBH, SpeciesCode) %>%
  drop_na() %>%
  mutate(lHeight = log(Height), glmfit = exp(fitted(glm2))) %>%
  ggplot(aes(x=DBH))+
  geom_bin_2d(aes(y = Height), bins = 25, drop = TRUE)+ 
  scale_fill_viridis(discrete = FALSE)+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  xlab("DBH (cm)") +
  ylab("Height") +
  ggtitle("Height vs DBH, Sardinilla")

```

### e: all species, DBH, fit a lm for log(height)- diameter

```{r}
glm3 <- lm(log(Height) ~ DBH, data = s_data)
```

```{r, echo = FALSE}
s_data %>%
  select(Height, DBH, lDBH, SpeciesCode) %>%
  drop_na() %>%
  mutate(lHeight = log(Height), glmfit = exp(fitted(glm3))) %>%
  ggplot(aes(x=DBH))+
  geom_point(aes(y=Height))+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "red")
```

### f: separate species, DBH, fit linear lm for log(height)-log(diameter)

```{r}
#linear
TR.dat <- s_data %>% 
  select(SpeciesCode, Height, lDBH) %>%
  filter(SpeciesCode == "TR") %>%
  drop_na()
glm2.TR <- lm(log(Height)~lDBH, TR.dat)
CM.dat <- s_data %>% 
  select(SpeciesCode, Height, lDBH) %>%
  filter(SpeciesCode == "CM") %>%
  drop_na()
glm2.CM <- lm(log(Height)~lDBH, CM.dat)
AE.dat <- s_data %>% 
  select(SpeciesCode, Height, lDBH) %>%
  filter(SpeciesCode == "AE") %>%
  drop_na()
glm2.AE <- lm(log(Height)~lDBH, AE.dat)
```

```{r, echo = FALSE}
#TR
TRglm2 <- s_data %>%
  select(Height, DBH, lDBH, SpeciesCode) %>%
  filter(SpeciesCode == "TR") %>%
  drop_na() %>%
  mutate(lHeight = log(Height), C = exp(chaveTest(DBH))*100, glmfit = exp(fitted(glm2.TR))) %>%
  ggplot(aes(x=DBH))+
  geom_bin_2d(aes(y = Height), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
  #geom_point(aes(y=Height))+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  geom_line(aes(y = C), color = "red" )+
  xlab("DBH (cm)") +
  ylab("Height") +
  ggtitle("TR: Ln Height vs DBH, Sardinilla")
#CM
CMglm2 <- s_data %>%
  select(Height, DBH, lDBH, SpeciesCode) %>%
  filter(SpeciesCode == "CM") %>%
  drop_na() %>%
  mutate(lHeight = log(Height),C = exp(chaveTest(DBH))*100, glmfit = exp(fitted(glm2.CM))) %>%
  ggplot(aes(x=DBH))+
  geom_bin_2d(aes(y = Height), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
  #geom_point(aes(y=Height))+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  geom_line(aes(y = C), color = "red" )+
  xlab("DBH (cm)") +
  ylab("Height") +
  ggtitle("CM: Ln Height vs DBH, Sardinilla")
#AE
AEglm2 <- s_data %>%
  select(Height, DBH, lDBH, SpeciesCode) %>%
  filter(SpeciesCode == "AE") %>%
  drop_na() %>%
  mutate(lHeight = log(Height), C = exp(chaveTest(DBH))*100, glmfit = exp(fitted(glm2.AE))) %>%
  ggplot(aes(x=DBH))+
  geom_bin_2d(aes(y = Height), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
  #geom_point(aes(y=Height))+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  geom_line(aes(y = C), color = "red" )+
  xlab("DBH (cm)") +
  ylab("Height") +
  ggtitle("AE: Ln Height vs DBH, Sardinilla")

Pglm2 <- s_data %>%
  select(Height, DBH, lDBH, SpeciesCode) %>%
  drop_na() %>%
  mutate(lHeight = log(Height), glmfit = exp(fitted(glm2))) %>%
  ggplot(aes(x=DBH))+
  geom_bin_2d(aes(y = Height), bins = 25, drop = TRUE)+ 
  scale_fill_viridis(discrete = FALSE)+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  xlab("DBH (cm)") +
  ylab("Height") +
  ggtitle("Height vs DBH, Sardinilla")

graph <- list(Pglm2, TRglm2, CMglm2, AEglm2)
#gridplot all 3
plot_grid(plotlist=graph, nrow = 2, ncol = 2)

```

### SUMMARY:

1.  Height- DBH All Species best: GLM2 lHeight \~ lDBH
2.  Height-DBH Different species Use same model: GLM2 lHeight \~ lDBH

## Testing Equations

```{r}
glm2Test <- function(D) {
  lH <- 5.4015 + 0.642*log(D)
  return(lH)
}

glm2_iTest <- function(D) {
  lH <- 4.9476 + 0.6902*log(D)
  return(lH)
}
```

## Testing GLM2 on Sardinilla data

$Log(H) = 5.4015 + 0.642*Log(D)$

$H = e^{(5.4015 + 0.642*Log(D))}$

TEST SET:

```{r, echo=FALSE}
df_t <- s_data %>% select(SpeciesCode, Height, DBH) %>% drop_na()
df_t$lH <- glm2Test(df_t$DBH)
df_t$H <- exp(df_t$lH)
df_t$ClH <- chaveTest(df_t$DBH)
df_t$CH <- exp(df_t$ClH)*100 #was in m
```

```{r, include = FALSE}
df_t %>%
ggplot(aes(x = DBH, y = Height, colors = SpeciesCode))+
geom_point()+
geom_line(aes(x = DBH, y= CH), color = 'red')+ #chave
geom_line(aes(x = DBH, y = H), linetype = 'dashed', color = 'blue')

```

```{r, echo = FALSE}
# Same plot but with data density
df_t %>% ggplot(aes(x = DBH, y = Height))+
geom_bin_2d(bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
geom_line(aes(x = DBH, y= CH), color = 'red')+
geom_line(aes(x = DBH, y = H), linetype = 'dashed', color = 'blue')

```

```{r}
df_t$lHeight <- log(df_t$Height)
```

```{r, echo = FALSE}
df_t %>%
ggplot(aes(x = DBH, y = lHeight, colors = SpeciesCode))+
geom_point()
```

# Ipeti data

```{r, include=FALSE}
i_data <- fread("../Data/baseline_table.csv")

i_data <- i_data %>%
  filter(survival != 0) %>% 
  select(-c("monotype", "owner"))
```

units unsure, we are assuming height in m and DBH in cm.

### Visualizing height - DBH

```{r, echo = FALSE}
i_data %>% 
filter(dbh != is.na(dbh)) %>%
select(spcode, height, dbh) %>%
mutate(height.cm = height*100) %>%
ggplot(aes(x = dbh, y = height.cm, color = spcode)) +
geom_point()+
xlab("DBH (cm)") +
ylab("Height (cm)") +
ggtitle("Height vs DBH IpetiData")
```

```{r, echo = FALSE}
i_data %>% 
filter(dbh != is.na(dbh)) %>%
select(spcode, height, dbh) %>%
mutate(height.cm = height*100, lheight.cm = log(height.cm)) %>%
ggplot(aes(x = dbh, y = lheight.cm, color = spcode)) +
geom_point()+
xlab("DBH (cm)") +
ylab("log(Height (cm))") +
ggtitle("Height vs DBH IpetiData")
```

```{r, echo = FALSE}
pltlist <- list()
for (i in unique(i_data$spcode)){
  if (nrow(i_data %>% filter(i_data$spcode == i)) < 500){
    next
  }else{
    plt <- i_data %>% 
      filter(dbh != is.na(dbh)) %>%
      select(spcode, height, dbh) %>%
      mutate(height.cm = height*100) %>%
      filter(spcode == i) %>%
      ggplot(aes(x = dbh, y = height.cm)) +
      geom_point()+
      xlab("DBH (cm)") +
      ylab("Height (cm)") +
      ggtitle(i)
    pltlist <- c(pltlist, list(plt))
  }
}
plot_grid(plotlist = pltlist, ncol = 3, nrow =4)
```

```{r, echo = FALSE}
pltlist <- list()
for (i in unique(i_data$spcode)){
  if (nrow(i_data %>% filter(i_data$spcode == i)) < 500){
    next
  }else{
    plt <- i_data %>% 
      filter(dbh != is.na(dbh)) %>%
      select(spcode, height, dbh) %>%
      mutate(height.cm = height*100, lheight.cm = log(height.cm)) %>%
      filter(spcode == i) %>%
      ggplot(aes(x = dbh, y = lheight.cm)) +
      geom_point()+
      xlab("DBH (cm)") +
      ylab("Height (cm)") +
      ggtitle(i)
    pltlist <- c(pltlist, list(plt))
  }
}
plot_grid(plotlist = pltlist, ncol = 3, nrow =4)
```

## Fitting Chave, Model on Ipeti Data

```{r}
i_data$glm2.lheight <- glm2Test(i_data$dbh)
i_data$glm2.height <- exp(i_data$glm2.lheight)
i_data$chave.lheight <- chaveTest(i_data$dbh)
i_data$chave.height <- exp(i_data$chave.lheight)*100 #was in m
```

Using normal data

```{r, echo = FALSE}
i_data %>%
mutate(height.cm = height*100) %>%
ggplot(aes(x = dbh, y = height.cm, colors = spcode))+
geom_point()+
geom_line(aes(x = dbh, y= chave.height), color = 'red')+
geom_line(aes(x = dbh, y = glm2.height), linetype = 'dashed', color = 'blue')
```

Data with density of points

```{r, echo = FALSE}
i_data %>%
mutate(height.cm = height*100) %>%
ggplot(aes(x = dbh))+
geom_bin_2d(aes(y = height.cm), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
geom_line(aes(y= chave.height), color = 'red')+
geom_line(aes(y = glm2.height), linetype = 'dashed', color = 'blue')
```

## fitting a glm on ipeti data

```{r}
i_data <- i_data %>% mutate(height.cm = height*100, ldbh = log(dbh), lheight.cm = log(height.cm))
i_data[is.na(i_data$lheight.cm) | is.na(i_data$dbh) | i_data=="Inf" | i_data == "-Inf"] = NA
glm2_i <- lm(lheight.cm~ldbh, data = i_data)
```

```{r, echo = FALSE}
i_data %>%
select(height.cm, dbh, ldbh, spcode, lheight.cm) %>%
filter(dbh != is.na(dbh) & lheight.cm != (is.na(lheight.cm))) %>%
mutate(lheight.cm = log(height.cm), glmfit = exp(fitted(glm2_i))) %>%
ggplot(aes(x=dbh))+
#geom_bin_2d(aes(y = height), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
geom_point(aes(y=height.cm))+
geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
xlab("DBH (cm)") +
ylab("Height (cm)") +
ggtitle("Height vs DBH, Ipeti")
```

```{r. echo = FALSE} 
i_data %>% 
  select(height.cm, dbh, ldbh, spcode, lheight.cm) %>% 
  filter(dbh != is.na(dbh) & lheight.cm != (is.na(lheight.cm))) %>%
  mutate(lheight.cm = log(height.cm), glmfit = exp(fitted(glm2_i))) %>%
  ggplot(aes(x=dbh))+
  geom_bin_2d(aes(y = height.cm), bins = 25, drop = TRUE) +
  scale_fill_viridis(discrete = FALSE) +
  geom_point(aes(y=height.cm))+ geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+ xlab("DBH (cm)") + ylab("Height (cm)") + ggtitle("Ln Height vs DBH, Ipeti")
```
# Combining Ipeti and Sardinilla data

```{r, include = FALSE}
i_data_r <- i_data %>% select(c("dbh", "height.cm", "spcode"))
s_data_r <- s_data %>% select(c("DBH", "Height", "SpeciesCode"))
colnames(s_data_r) <- c("dbh", "height.cm", "spcode")

data <- rbind(i_data_r, s_data_r) %>% na.omit()
```

visualising data - height vs dbh

```{r, echo = FALSE}
data %>% 
ggplot(aes(x = dbh, y = height.cm, color = spcode)) +
geom_point()+
xlab("DBH (cm)") +
ylab("Height (cm)") +
ggtitle("Height vs DBH: Ipeti and Sardinilla Data")
```

visualising data - lheight vs dbh

```{r, echo = FALSE}
data %>% 
mutate(lheight.cm = log(height.cm)) %>%
ggplot(aes(x = dbh, y = lheight.cm, color = spcode)) +
geom_point()+
xlab("DBH (cm)") +
ylab("log(Height (cm))") +
ggtitle("Height vs DBH: Ipeti and Sardinilla Data")
```

visualising data - lheight vs ldbh

```{r, echp = FALSE}
data %>% 
mutate(ldbh = log(dbh), lheight.cm = log(height.cm)) %>%
ggplot(aes(x = ldbh, y = lheight.cm, color = spcode)) +
geom_point()+
xlab("DBH (cm)") +
ylab("log(Height (cm))") +
ggtitle("Height vs DBH: Ipeti and Sardinilla Data")
```

## GLMS

log(height) vs dbh

```{r}
data$lheight.cm <- log(data$height.cm)
data$ldbh <- log(data$dbh)
data[is.na(data$lheight.cm) |is.na(data$ldbh) |data =="Inf" | data == "-Inf"] = NA
glm <- lm(lheight.cm ~ ldbh, data = data, na.action = "na.exclude")
```

```{r, echo = FALSE}
data %>%
  mutate(glmfit = exp(fitted(glm))) %>%
  ggplot(aes(x=dbh))+
  #geom_bin_2d(aes(y = height.cm), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
  geom_point(aes(y=height.cm))+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  xlab("DBH (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH, Ipeti and Sardinilla")
```

```{r, echo = FALSE}
data %>%
  mutate(glmfit = fitted(glm)) %>%
  ggplot(aes(x=dbh))+
  #geom_bin_2d(aes(y = height.cm), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
  geom_point(aes(y=lheight.cm))+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  xlab("DBH (cm)") +
  ylab("log(Height (cm))") +
  ggtitle("Height vs DBH, Ipeti and Sardinilla")
```

```{r, echo = FALSE}
data %>%
  mutate(glmfit = exp(fitted(glm))) %>%
  ggplot(aes(x=dbh))+
  geom_bin_2d(aes(y = height.cm), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  xlab("DBH (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH, Ipeti and Sardinilla")
```

```{r, echo=FALSE}
data %>%
  mutate(glmfit = fitted(glm)) %>%
  ggplot(aes(x=dbh))+
  geom_bin_2d(aes(y = lheight.cm), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
  geom_line(aes(y=glmfit), linetype = "dashed", color = "blue")+
  xlab("DBH (cm)") +
  ylab("log(Height (cm))") +
  ggtitle("Height vs DBH, Ipeti and Sardinilla")
```

# SUMMARY: all results

Models:

```{r}
data$glm2.lheight <- glm2Test(data$dbh)
data$glm2.height <- exp(data$glm2.lheight)
data$chave.lheight <- chaveTest(data$dbh)
data$chave.height <- exp(data$chave.lheight)*100 #was in m
data$glm2_i.lheight <- glm2_iTest(data$dbh)
data$glm2_i.height <- exp(data$glm2_i.lheight)
```

```{r, echo = FALSE, fig.cap = "Blue for glm, red for Chave, green for glm2, cyan for glm2_i" }
data %>%
  mutate(glmfit = exp(fitted(glm))) %>%
  ggplot(aes(x=dbh))+
  geom_point(aes(y=height.cm))+
  geom_line(aes(y=glmfit), color = "blue")+
  geom_line(aes(y= chave.height), linetype = 'dashed', color = 'red')+
  geom_line(aes(y = glm2.height), linetype = 'dashed', color = 'green')+
  geom_line(aes(y = glm2_i.height), linetype = 'dashed', color = 'cyan')+
  xlab("DBH (cm)") +
  ylab("Height (cm)") +
  ggtitle("Height vs DBH, Ipeti and Sardinilla")
```

```{r., echo = FALSE, "Blue for glm, red for Chave, green for glm2, cyan for glm2_i"} 
data %>%   
  mutate(glmfit = exp(fitted(glm))) %>%  
  ggplot(aes(x=dbh))+   
  geom_bin_2d(aes(y = height.cm), bins = 50, drop = TRUE) + 
  scale_fill_viridis(discrete = FALSE)+   
  geom_line(aes(y=glmfit), color = "blue")+   
  geom_line(aes(y= chave.height), linetype = 'dashed', color = 'red')+  
  geom_line(aes(y = glm2.height), linetype = 'dashed', color = 'green')+   
  geom_line(aes(y = glm2_i.height), linetype = 'dashed', color = 'cyan')+   
  xlab("DBH (cm)") +   
  ylab("Height (cm)") +  
  ggtitle("Height vs DBH, Ipeti and Sardinilla")`
```

```{r, echo = FALSE}
data %>%
  mutate(glmfit = fitted(glm), ldbh = log(dbh)) %>%
  ggplot(aes(x=ldbh))+
  geom_bin_2d(aes(y = lheight.cm), bins = 25, drop = TRUE) + scale_fill_viridis(discrete = FALSE)+
  geom_line(aes(y=glmfit), color = "blue")+
  geom_line(aes(y= chave.lheight), linetype = 'dashed', color = 'red')+
  geom_line(aes(y = glm2.lheight), linetype = 'dashed', color = 'green')+
  geom_line(aes(y = glm2_i.lheight), linetype = 'dashed', color = 'cyan')+
  xlab("log(DBH (cm))") +
  ylab("g(Height (cm))") +
  ggtitle("Height vs DBH, Ipeti and Sardinilla")
```

Final model: GLM2